\thispagestyle{empty}
\setsection{ABSTRACT}

\sloppy

\noindent Context: In Agile software development environments, organizations typically use multiple separate tools for project management, internal communication, and online meetings. This leads to scattered user information, project data, and documents, making centralized monitoring, progress tracking, and effective data utilization challenging. Therefore, a central platform is needed to serve as a connecting hub that unifies the entire system, helping organizations manage all activities more coherently and efficiently.

\noindent Objective: This thesis builds a central platform for an AI-integrated Agile project management system. The platform provides user account and workspace management, an administrative interface for workspace managers, shared document storage, a centralized notification system, and an intelligent AI assistant that automatically aggregates information from project management, communication, and meeting subsystems to generate reports supporting monitoring and decision-making.

\noindent Methodology: The platform is built on a microservice architecture with independent services communicating via APIs, including: an API Gateway handling authentication, authorization, and request routing; an administrative interface developed with React/Next.js; a centralized file storage service; a notification system that collects and distributes information from subsystems; and an AI service integrated with third-party providers for data analysis. The system uses a relational database for account and workspace management, combined with cloud storage for files. The architecture is designed for scalability and maintainability.

\noindent Results: The completed product allows users to register, log in, and access all system features through a central gateway. Workspace managers can easily manage members, configure workspaces, monitor notifications, and view reports through an intuitive interface. The notification system ensures important information from project management, team chat, and meetings is delivered to the right people at the right time. Notably, the integrated AI assistant collects data from project activities and generates concise summaries and reports, helping managers quickly grasp the situation without checking each system separately.

\noindent Conclusion: The central platform has been successfully built, serving as the backbone of the Agile project management system. The product helps organizations reduce complexity when using multiple separate tools while creating a unified work environment. With flexible scalability and an integrated AI assistant, the platform provides a solid foundation for expanding decision support and data analysis features in the future.

\fussy
